Article title

### 2017-06-28 paper-webserver.tex
CHANGE: collapse para 3 and 4 together

Here we present Spfy, a platform bundling subtyping modules and machine-learning predictions for \textit{E. coli}, built using modern containerization of services, task queues for parallelizing analyses, and exception handling throughout. Spfy offers serotype predictions, identification of antimicrobial resistance genes through the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and statistical or machine-learning based comparisons of groups based on user-selected restrictions. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

>>>>

Previously, we developed Superphy \cite{whiteside2016superphy} a online platform, targeting \textit{E. coli}, which determines Shiga toxin subtypes, AMR genes through the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and statistical significance tests between subgroups in associated metadata. Here we present Spfy, a complete rewrite of Superphy integrating our Panseq package \cite{laing2010pan} for pan-genomic analyses of accessory regions, long-term storage of results in a graph database, and containerization of services using Docker, a modern approach found in many web servers and proposed to mitigate the complexities of bioinformatic pipelines \cite{di2015impact}. Furthermore, Spfy takes a modular approach to tool integration and distributes analyses over a task queue, allowing modules to run in parallel. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.
